Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Finally, the full extent of chatbot technology is not really examined in these
surveys. They can be connected to natural language processing engines with
sentiment analysis as well as other analytics. Examining the mood of the class
such as responses to new materials, assignments, exams or external events will
help any student-centered teaching strategy, which will also help students (and
teachers) achieve their learning objectives. This line of work, however, would
require the introduction of some pilot study combined with initial opinion
assessments from students and is thus left for the future.

>>>>

Finally, the full extent of chatbot technology is not really examined in these
surveys. They can be connected to natural language processing engines with
sentiment analysis as well as other analytics. Examining the mood of the class
such as responses to new materials, assignments, exams or external events will
help any student-centered teaching strategy, which will also help students (and
teachers) achieve their learning objectives. This line of work, however, would
require the introduction of some pilot study combined with initial opinion
assessments from students and is thus left as future work.
